Multi-Robot Probabilistic Mapping and Exploration

### 2018-07-11 Dissertation/Defense/defense.tex
added recent figs to dissertation, minor edits to defense

\institute{\footnotesize
{\normalsize Evan Kaufman\\Research Advisor: Taeyoung Lee}\vspace*{0.1cm}\\
  Mechanical and Aerospace Engineering\\ George Washington University \vspace*{0.3cm}\\ {\normalsize Special Thanks to:\\
 \vspace*{0.2cm}
 Kuya Takami, Mahdis Bisheban, and Kanishke Gamagedara} \\Department of Mechanical Engineering\\George Washington University\\
\vspace*{0.2cm}
{\normalsize Zhuming Ai, Ira. S. Moskowitz, and Mark Livingston}\\Information Management \& Decision Architectures\\U.S. Naval Research Laboratory}

@@

\begin{frame}
\frametitle{Outline}
\begin{itemize}
	\item Occupancy Grid Mapping
	\begin{itemize}
		\item Background and problem definition
		\item Common approaches and approximations
		\item Inverse sensor model in 1D
		\item Ray casting for 2D and 3D environments
		\item Numerical examples
	\end{itemize}
	\pause
	\item Autonomous Exploration
	\begin{itemize}
		\item Existing solutions: frontiers, expected measurements
		\item Proposed approach: entropy expectation
		\item Collision-free trajectories
		\item Optimal pose selection
		\item Numerical Examples
	\end{itemize}
\end{itemize}
\end{frame}

>>>>

\institute{\footnotesize
{\normalsize Evan Kaufman\\
\vspace*{0.2cm}
Dissertation Director: Taeyoung Lee}\\
\vspace*{0.3cm}
{\normalsize Committee Members:\\
 \vspace*{0.2cm}
Taeyoung Lee, James Hahn, Robert Pless,\\Chung-Hyuk Park, and Zhuming Ai}
\vspace*{0.4cm}\\
  Mechanical and Aerospace Engineering\\George Washington University
}

%\institute{\footnotesize
%{\normalsize Evan Kaufman\\Research Advisor: Taeyoung Lee}\vspace*{0.1cm}\\
%  Mechanical and Aerospace Engineering\\ George Washington University \vspace*{0.3cm}\\ {\normalsize Special Thanks to:\\
% \vspace*{0.2cm}
% Kuya Takami, Mahdis Bisheban, and Kanishke Gamagedara} \\Department of Mechanical Engineering\\George Washington University\\
%\vspace*{0.2cm}
%{\normalsize Zhuming Ai, Ira. S. Moskowitz, and Mark Livingston}\\Information Management \& Decision Architectures\\U.S. Naval Research Laboratory}

@@

\begin{frame}
\frametitle{Outline}
\begin{itemize}
	\item Occupancy Grid Mapping
	\begin{itemize}
		\item Background and problem definition
		\item Common approaches and approximations
		\item Inverse sensor model in 1D
		\item Ray casting and measurement scans for 2D and 3D environments
		\item Numerical examples
	\end{itemize}
	\pause
	\item Autonomous Exploration
	\begin{itemize}
		\item Existing solutions: frontiers, expected measurements
		\item Proposed approach: entropy expectation
		\item Collision-free trajectories
		\item Optimal pose selection
		\item Numerical Examples
	\end{itemize}
\end{itemize}
\end{frame}

### 2018-07-11 Dissertation/Thesis/tex/results.tex
added recent figs to dissertation, minor edits to defense

A key improvement to prior experiments is the ability to consider the occupancy properties in full 3D. This allows the robot to understand that the mannequin occupies some space that the robot must avoid. However, the robot also recognizes that the space above the mannequin is free, and it chooses a trajectory above the mannequin to reach new terrain. At other times, the robot observes spaces from lower vantage points, which can be advantageous with a short sensor range and the forward direction of the Asus Xtion. These added capabilities are attributed to the full 3D mapping and exploration approach.

@@

>>>>

A key improvement to prior experiments is the ability to consider the occupancy properties in full 3D. This allows the robot to understand that the mannequin occupies some space that the robot must avoid. However, the robot also recognizes that the space above the mannequin is free, and it chooses a trajectory above the mannequin to reach new terrain. At other times, the robot observes spaces from lower vantage points, which can be advantageous with a short sensor range and the forward direction of the Asus Xtion relative to the robot. These added capabilities are attributed to the full 3D mapping and exploration approach.

@@

The controller is also highly important for following autonomous exploration trajectories accurately. The geometric controller tracks the desired trajectory to avoid collsions with obstacles in the room. The plot of 3D position is shown in Figure \ref{fig:Explore3D_x3D} and the desired commands and measured outputs of the controlled system are shown in Figures \ref{fig:Explore3D_x_xd}, \ref{fig:Explore3D_v_vd}, \ref{fig:Explore3D_R_Rd}, and \ref{fig:Explore3D_W_Wd}, and the total propeller force $f$ from \refeqn{geometricf} and moment $M$ from \refeqn{geometricM} are shown in Figure \ref{fig:Explore3D_fM}. An interesting aspect is that at $1.31$ min, the robot temporarily obtains a poor estimate of the robot, but since this is short-lived, the robot quickly recovers and continues exploring. In summary, geometric control successfully tracks the desired commands from autonomous exploration through uncertain environments.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{explore3D_x3D.pdf}
	\caption{Robot Position over Full 3D Experiment}
	\medskip
	\small
	The history of robot position is shown in 3D with respect to a north-east-down world-fixed frame, such that there are all negative $x_3$ values, making the trajectory appear upside-down. The low locations (high relative to the ground) on the left of the figure ($x_1\approx-1$ m, $x_2\approx0.5$ m, and $x_3\approx-1.8$ m) correspond to flying over the mannequin.
	\label{fig:Explore3D_x3D}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{explore3D_x_xd.pdf}
	\caption{Geometric Control Position Tracking over Full 3D Experiment}
	\medskip
	\small
	The position of the robot (blue solid) tracks the desired position (red dashed) over the experiment.
	\label{fig:Explore3D_x_xd}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{explore3D_v_vd.pdf}
	\caption{Geometric Control Velocity Tracking over Full 3D Experiment}
	\medskip
	\small
	The velocity of the robot (blue solid) tracks the desired velocity (red dashed) over the experiment.
	\label{fig:Explore3D_v_vd}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{explore3D_R_Rd.pdf}
	\caption{Geometric Control Attitude Tracking over Full 3D Experiment}
	\medskip
	\small
	The attitude of the robot (blue solid), shown with the rotation matrix between the north-east-down frame and the body-fixed frame, tracks the desired attitude (red dashed) over the experiment. The bottom-right plot shows the third body-fixed axis is mostly-aligned with the third world-fixed axis, which corresponds to maintaining level flight.
	\label{fig:Explore3D_R_Rd}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{explore3D_W_Wd.pdf}
	\caption{Geometric Control Angular Velocity Tracking over Full 3D Experiment}
	\medskip
	\small
	The angular velocity of the robot (blue solid) tracks the desired angular velocity (red dashed) over the experiment. The overall larger $\Omega_3$ corresponds to yaw rotation to change the direction of the Xtion depth sensor.
	\label{fig:Explore3D_W_Wd}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{explore3D_fM.pdf}
	\caption{Geometric Control Force and Moments over Full 3D Experiment}
	\medskip
	\small
	The forces and moments provided by the geometric control are shown over the experiment. The values of $f$ remain largely-steady to cancel gravitational forces. Changes in $M_1$ and $M_2$ correspond to roll and pitch movements to move around horizontally. Changes in $M_3$ correspond to correcting yaw for the Xtion direction.
	\label{fig:Explore3D_fM}
\end{figure}
